Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-10-04 paper/paper.tex
another Discussion paragraph

\jdbcomment{Our results demonstrate that the single-cell viral genetic information provided by this methodological advance is extremely valuable for understanding the biology of influenza infection, especially as it relates to innate-immune detection.}

\jdbcomment{It also confirms the suggestion by \citet{sjaastad2018distinct} that viral genetic variation contributes to the variability in gene expression among IFN+ cells.}

>>>>

Our results also indicate that different types of viral defects induce IFN by somewhat different processes.
For instance, higher viral gene transcription is associated with IFN induction only in cells that are infected by virions with deficiencies in NS.
This finding is consistent with the suggestion by \citet{sjaastad2018distinct} that viral genetic variation contributes to cell-to-cell variability in the expression of anti-viral genes.
Larger-scale studies similar to the one performed here should be useful for further determining the extent that virions with different defects cause cells to trigger distinct transcriptional programs.

\jdbcomment{But results also show that non-viral factors are clearly important.}

\jdbcomment{summary paragraph}
